Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-02-09 article.tex
Section 4

This section focus on the pattern containment problem
in case only the pattern $\sigma$ avoids $231$ and $213$.

@@

\begin{proof}
We consider the following problem :\\
Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\

$
\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
\begin{cases}
	true 	& \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
			& \text{with every element in}\\
			&[\min,\max]\\
>>>>>>> f9bc0a20a19c155782e9e48e9d01a9fb6f3718ac

	false 	& otherwise\\
\end{cases}
$

$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}$ is closed under induction.
it can be solved by means of the following relations:\\

>>>>

This section focuses on the pattern containment problem
in case only the pattern $\sigma$ avoids $231$ and $213$.
We need to consider a specific decomposition $F$ of $\sigma$ into factors.
For $\sigma \in S_k$, the factorization
$\sigma = F(p) F(p-1) \ldots F(1)$ is defined as follows:
(i) $\sigma[k]$ is the last letter of $F(1)$,
(ii) for every $1 \leq i < k$,
if $s_\sigma[i] = s_\sigma[i+1]$ then
$\sigma[i]\sigma[i+1]$ is part of the same factor.
For every factor $F(j)$ of the decomposition, we let
$L(j)$ stand for the leftmost letter of $F(j)$.
For example,
for $\sigma = 981237654$,
we have
$\sigma = F(4) F(2) F(1)$ with
$F(1) =7654$, $F(2) = 123$ and $F(3) = 98$.
Furthermore,
$L(1) = 7$, $L(2) = 1$ and $L(3) = 9$.

@@

\begin{proof}
We consider the following problem :\\
Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\
$$
\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
\begin{cases}
	true 	& \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
			  & \text{with every element in $[\min,\max]$}\\
	false 	& otherwise\\
\end{cases}
$$
$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}$ is closed under induction.
It can be solved by means of the following relations:\\
